Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-02-03 paper/paper.tex
something on cifar10

% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse

% hinting at overfitting/regularization effects of masking and sparsification

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune.pdf}
    % \caption{} \label{fig:log-alpha-kde}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/sum__fashion-mnist__fine-tune.pdf}
    % \caption{} \label{fig:log-alpha-proba}
  \end{subfigure}
  \caption{%
    The accuracy-compression trade-off after ``fine-tune''.
    \textit{top}: MNIST \citep{citation_needed};
    \textit{bottom}: Fashion MNIST \citep{citation_needed}.
  }
  \label{fig:mnist-like_trade-off}
\end{figure}

The same approach was applied to
CIFAR10 (sec.~\ref{sub:cifar10_100} experiments, which could partly explain the overall
poor test performance we got from the tested VGG16 model ($\real$ and $\cplx$ version).

% comparison strategy
We conduct a moderately sized numerical experiment on MNIST and similar $28\times 28$
greyscale image datasets to see whether the proposed $\cplx$-variational dropout indeed
sparsifies complex-valued networks. We compare with the studied $\cplx$-valued networks
against their $\real$-valued counterparts both in terms of the resulting sparsity and
test performance. For a fair comparison, we make the $\cplx$-valued network have
approximately half as many parameters, \citep{monning_evaluation_2018}.

Although image data is not $\cplx$ in nature \citet{trabelsi_deep_2017} study the applicability
of $\cplx$-valued networks to image classification (CIFAR-10, CIFAR-100, and a subset of
SVHN). Their approach is to either embed $\real$ in $\cplx$ (by $\Re z = 0$), or train
a smaller auxiliary network, that synthesizes the imaginary component from the raw channel
data. In our experiments we apply the two-dimensional Fourier Transform to get $\cplx$-valued
inputs. We concede that this is a rather unnatural representation of image data, however
the selection of publicly available datasets, which are not artificially $\cplx$-valued,
is limited to audio signals.

Indeed, as is shown by the numerical experiments on MNIST-like datasets and CIFAR10, a
real-valued model trained on the Fourier transformed data underperforms relative to
its architectural twin, fit to on the raw colour data. At the same time complex-valued
models.

@@

\subsection{CIFAR10/100} % (fold)
\label{sub:cifar10_100}

% mention the same experimental setup as in MNIST
% describe the VGG16 model and its cplx-valued modification
% mention that fourier-features perfomed worse than raw image data embeded in to $\cplx$
% compare compressed cplx-vgg against real-vgg
% draw some conclusions

>>>>

% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
Figures~\ref{fig:mnist-like__trade-off__vd} and ~\ref{fig:mnist-like__trade-off__ard} show
the results on the ``MNIST'' dataset for $\tau\in\{-\tfrac12, \tfrac32\}$ and $
  C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
$ replicated $5$ times using the method from sec.~\ref{ssub:variational_dropout} (VD)
and~\ref{ssub:empirical_bayes} (ARD), respectively (results for other MNIST-like datasets
are in the appendix).

% discussion of TwoLayerDenseModel
% discussion of SimpleConvModel
% hinting at overfitting/regularization effects of masking and sparsification

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__TwoLayerDenseModelVD.pdf}
    % \caption{} \label{fig:log-alpha-kde}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__SimpleConvModelVD.pdf}
    % \caption{} \label{fig:log-alpha-proba}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
    (top) and \textit{SimpleConvModel} (bottom) for method in sec.~\ref{ssub:variational_dropout}.
  }
  \label{fig:mnist-like__trade-off__vd}
\end{figure}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__TwoLayerDenseModelARD.pdf}
    % \caption{} \label{fig:log-alpha-kde}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__SimpleConvModelARD.pdf}
    % \caption{} \label{fig:log-alpha-proba}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
    (top) and \textit{SimpleConvModel} (bottom) for method in sec.~\ref{ssub:empirical_bayes}.
  }
  \label{fig:mnist-like__trade-off__ard}
\end{figure}

% which is better ARD or VD
It is worth pointing out that the prior used in ARD models offers slightly more favourable
compression-accuracy values, matching the established perception that log-uniform prior
is \todo{too harsh for sparsification tasks}, \citep{kharitonov_variational_2018}.

% hopeful conclusion
\todo{The numerical experiments on MNIST-like datasets} demonstrate, that models using fourier
features perform poorly in comparison to models using raw image input.

@@

\subsection{CIFAR10} % (fold)
\label{sub:cifar10}

% mention the same experimental setup as in MNIST
Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
that we study VGG16 model, \citep{citation_needed}, and its $\cplx$-counterpart, fit
on the full training split of $60k$ colour $32\times32$ images, and use only raw image
input features (\texttt{raw}).

% describe the VGG16 model and its cplx-valued modification
The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers
replaced by their $\cplx$-valued versions. To maintain comparability, we half the filter
sizes of $\cplx$ model.

% mention that fourier-features perfomed worse than raw image data embeded in to $\cplx$

% compare compressed cplx-vgg against real-vgg

% draw some conclusions
